RTS AI: Problems and Techniques

### 2015-08-18 ECGG_RTSProblems/ECGG_RTSProblems.tex
Add Synonyms and Definition

\section{Introduction}\label{sec:intro}
The  field of  Real-Time Strategy  (RTS) game  Artificial Intelligence
(AI) has advanced significantly in the past few years, partially thanks to competitions as the ``ORTS
RTS  Game AI  Competition''  (held  from 2006  to  2009), the  ``AIIDE
StarCraft AI Competition'' (held since  2010), and the ``CIG StarCraft
RTS AI Competition'' (held since  2011). Based on the work work presented in \cite{ontanon2013survey}, here we first define RTS games, then list the open problems in creating AI for RTS games, and finally point to the approaches that have been proposed to address these problems.

@@

\section{Real-Time Strategy Games}\label{sec:rts}

{\em Real-Time Strategy} (RTS) is a sub-genre of strategy games where players need
to  build an  economy (gathering  resources and  building a  base) and
military power (training units  and researching technologies) in order
to defeat  their opponents  (destroying their army  and base).  From a
theoretical point of view, the  main differences between RTS games and
traditional board games such as Chess are:

@@

\section{Challenges in RTS Game AI}\label{subsec:challenges}

@@

\section{Existing work on RTS Game AI}\label{sec:review}

@@

\section{Conclusions}

>>>>

\section*{Synonyms}

Real-Time Strategy games; RTS games; Artificial Intelligence; AI; Game AI

\section*{Definition}

{\em Real-Time Strategy} (RTS) games  is a sub-genre of strategy games
where  players  need to  build  an  economy (gathering  resources  and
building a  base) and military  power (training units  and researching
technologies)  in order  to defeat  their opponents  (destroying their
army and base).  Artificial Intelligence problems related to RTS games
deal with  the behavior of  an artificial player. This  consists among
others to learn  how to play, to have an  understanding about the game
and  its environment,  to predict  and  infer game  situations from  a
context and sparse information.

\section*{Introduction}\label{sec:intro}
The  field of  Real-Time Strategy  (RTS) game  Artificial Intelligence
(AI) has advanced significantly in the past few years, partially thanks to competitions as the ``ORTS
RTS  Game AI  Competition''  (held  from 2006  to  2009), the  ``AIIDE
StarCraft AI Competition'' (held since  2010), and the ``CIG StarCraft
RTS AI Competition'' (held since  2011). Based on the work work presented in \cite{ontanon2013survey}, here we first define RTS games, then list the open problems in creating AI for RTS games, and finally point to the approaches that have been proposed to address these problems.

@@

\section*{Real-Time Strategy Games}\label{sec:rts}

From a  theoretical point  of view, the  main differences  between RTS
games and traditional board games such as Chess are:

@@

\section*{Challenges in RTS Game AI}\label{subsec:challenges}

@@

\section*{Existing work on RTS Game AI}\label{sec:review}

@@

\section*{Conclusions}
